A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-01-31 paper.tex
add wmo

%%% Acronyms
\newacronym{sres}{SRES}{Special Report on Emissions Scenarios}
\newacronym{cmip6}{CMIP6}{Coupled Model Intercomparison Project (Phase 6)}
\newacronym{smip}{ScenarioMIP}{Scenario Model Intercomparison Project}
\newacronym{ceds}{CEDS}{Community Emissions Data System}
\newacronym{esm}{ESM}{Earth System Model}
\newacronym{luc}{LUC}{Land-use Change}
\newacronym{luluc}{LULUC}{Land-use and Land-use Change}
\newacronym{weu}{WEU}{Western Europe}
\newacronym{nam}{NAM}{North America}
\newacronym{pao}{PAO}{Pacific OECD}
\newacronym{eeu}{EEU}{Central and Eastern Europe}
\newacronym{fsu}{FSU}{Former Soviet Union}
\newacronym{pas}{PAS}{Other Pacific Asia}
\newacronym{cpa}{CPA}{Centrally-planned Asia and China}
\newacronym{sas}{SAS}{South Asia}
\newacronym{mea}{MEA}{Middle East and North Africa}
\newacronym{afr}{AFR}{Sub-Saharan Africa}
\newacronym{lam}{LAM}{Latin America and the Caribbean}
\newacronym{cli}{CLI}{Command Line Interface}

@@

The full harmonization workflow, outlined in Figure \ref{fig:workflow}, begins
by cleaning input data, which adds (null) model trajectories that exist in the
historical data set but are not provided by the model input and detects any
issues that would cause the harmonization process to fail. The methods used to
harmonize the data are then determined and the harmonization process is
executed. Upon completion of the harmonization process, aggregation of common
analysis regions is performed. A common regional aggregation used in the
\gls{iam} community was defined in the \glspl{rcp}
\cite{vuuren_representative_2011}, shown in Figure \ref{fig:regions}. Finally,
any exogenous trajectories the user provides are added. Exogenous trajectories
are normally provided for unmodeled gases with well-accepted scenario
trajectories, e.g., chlorofluorocarbons provided by WMO \cite{wmo2014}. Upon
completion, the harmonized trajectories and meta data regarding the
harmonization process are returned. A description of all returned meta data is
provided in Table \ref{tab:metadata}.

>>>>

%%% Acronyms
\newacronym{sres}{SRES}{Special Report on Emissions Scenarios}
\newacronym{cmip6}{CMIP6}{Coupled Model Intercomparison Project (Phase 6)}
\newacronym{smip}{ScenarioMIP}{Scenario Model Intercomparison Project}
\newacronym{ceds}{CEDS}{Community Emissions Data System}
\newacronym{esm}{ESM}{Earth System Model}
\newacronym{luc}{LUC}{Land-use Change}
\newacronym{luluc}{LULUC}{Land-use and Land-use Change}
\newacronym{weu}{WEU}{Western Europe}
\newacronym{nam}{NAM}{North America}
\newacronym{pao}{PAO}{Pacific OECD}
\newacronym{eeu}{EEU}{Central and Eastern Europe}
\newacronym{fsu}{FSU}{Former Soviet Union}
\newacronym{pas}{PAS}{Other Pacific Asia}
\newacronym{cpa}{CPA}{Centrally-planned Asia and China}
\newacronym{sas}{SAS}{South Asia}
\newacronym{mea}{MEA}{Middle East and North Africa}
\newacronym{afr}{AFR}{Sub-Saharan Africa}
\newacronym{lam}{LAM}{Latin America and the Caribbean}
\newacronym{cli}{CLI}{Command Line Interface}
\newacronym{wmo}{WMO}{World Meteorological Organization}

@@

The full harmonization workflow, outlined in Figure \ref{fig:workflow}, begins
by cleaning input data, which adds (0-valued) model trajectories that exist in
the historical data set but are not provided by the model input and detects any
issues that would cause the harmonization process to fail. The methods used to
harmonize the data are then determined and the harmonization process is
executed. Upon completion of the harmonization process, aggregation of common
analysis regions is performed. A common regional aggregation used in the
\gls{iam} community was defined in the \glspl{rcp}
\cite{vuuren_representative_2011}, shown in Figure \ref{fig:regions}. Finally,
any exogenous trajectories the user provides are added. Exogenous trajectories
are normally provided for unmodeled gases with well-accepted scenario
trajectories, e.g., chlorofluorocarbons provided by the \gls{wmo}
\cite{wmo2014}. Upon completion, the harmonized trajectories and meta data
regarding the harmonization process are returned. A description of all returned
meta data is provided in Table \ref{tab:metadata}.
